---
title: "R Notebook"
output: 
---

```{r}
setwd("~/Documents/SFSU.FALL.2017/424/R/R/Exercises&Examples")
load("ROADBIDS.Rdata")
View(ROADBIDS)
model = glm(ROADBIDS$STATUS~ROADBIDS$NUMBIDS+ROADBIDS$DOTEST, family = binomial(link="logit"))
summary(model)
```
"
```{r}
load("PACGEESE.Rdata")
```

```{r}
model <- glm(RESPONSE~ALTITUDE+LATERAL, family = binomial(link = 'logit'),data = PACGEESE)

summary(model)
anova(model, test = "Chisq")
1-pchisq(model$null.deviance-model$deviance, model$df.null-model$df.residual)
  newdata = data.frame(ALTITUDE=6, LATERAL=3)
predict(model,newdata,type="response")
logLik(model)

```
b) We reject the null hypothesis for this test and say that using $\alpha=0.01$, we can say that the   flight response time of the geese is dependant on the altitude of the helicopter. $\beta_{1_{zscore}}$ = 2.914, with an accompanying p-value of p=0.00357, which is below our given $\alpha$. 

c) Based on the model summary, we can reject the null hypothesis and state that the response time of the geese is dependent on the lateral distance of the helicopter. the $\beta_2$ z-score is -10.625, with a p-value of <2e-16, which is far below (<<) $\alpha = 0.01$.

```{r}
load("MTBE.Rdata")
```


```{r}
wellclass <- MTBE$WellClass
aquifer <- MTBE$Aquifier
ph <- MTBE$pH
welldepth <- MTBE$Depth
do2 <- MTBE$DissOxy
d2f <- MTBE$Distance
pind <- MTBE$IndPct
detet <- MTBE$MTBEDetect
levels(detet) = c(0,1)
detet

model <- glm( detet ~ wellclass+aquifer+ph+welldepth+do2+d2f+pind, family = binomial(link = 'logit'))
par(mfrow=c(2,2))
plot(model)
summary(model)
1-pchisq(model$null.deviance-model$deviance, model$df.null-model$df.residual)
#suggested model
model <- glm( detet~ wellclass+ph+welldepth, family = binomial(link = 'logit'))
summary(model)
par(mfrow=c(2,2))
plot(model)
logLik(model)
1-pchisq(model$null.deviance-model$deviance, model$df.null-model$df.residual)
```

#28
```{r}
load("BONDING.Rdata")
View(BONDING)
```

```{r}
#smartbond = 1 , composite = 0
#BONDING$ADHESIVE
adhesive <- as.numeric(as.factor(BONDING$ADHESIVE))-1
adhesive
model = glm(BONDING$ADHESIVE~BONDING$ARISCORE, family = binomial(link = "logit"))
summary(model)
1-pchisq(model$null.deviance-model$deviance, model$df.null-model$df.residual)
logLik(model)
```
