---
title: "R Notebook"
output: 
---

```{r}
setwd("~/Documents/SFSU.FALL.2017/424/R/R/Exercises&Examples")
load("ROADBIDS.Rdata")
View(ROADBIDS)
```

```{r}
load("PACGEESE.Rdata")
```

```{r}
model <- glm(RESPONSE~ALTITUDE+LATERAL, family = binomial(link = 'logit'),data = PACGEESE)

summary(model)
#how to determine adequacy in the model??? chi-squared test?????
anova(model, test = "Chisq")
pchisq(model$deviance, model$df.residual)
newdata = data.frame(ALTITUDE=6, LATERAL=3)
predict(model,newdata,type="response")
```
b) We reject the null hypothesis for this test and say that using $\alpha=0.01$, we can say that the   flight response time of the geese is dependant on the altitude of the helicopter. $\beta_{1_{zscore}}$ = 2.914, with an accompanying p-value of p=0.00357, which is below our given $\alpha$. 

c) Based on the model summary, we can reject the null hypothesis and state that the response time of the geese is dependent on the lateral distance of the helicopter. the $\beta_2$ z-score is -10.625, with a p-value of <2e-16, which is far below (<<) $\alpha = 0.01$.

```{r}
load("MTBE.Rdata")
View(MTBE)
library(olsrr)
```


```{r}
wellclass <- MTBE$WellClass                                      
aquafer <- MTBE$Aquifier
ph <- MTBE$pH
welldepth <- MTBE$Depth
do2 <- MTBE$DissOxy
d2f <- MTBE$Distance
pind <- MTBE$IndPct
detet <- MTBE$MTBEDetect
factor(wellclass)
wellclass <- as.numeric(as.factor(wellclass)) - 1
aquafer <- as.numeric(as.factor(aquafer)) - 1                                                                               
detet <- as.numeric(as.factor(detet)) - 1
mtbe.lmCoded <- lm(detet ~ wellclass+aquafer+ph+welldepth+do2+d2f+pind)
step(mtbe.lmCoded,direction='both')
```

```{r}
wellclass <- MTBE$WellClass   
wellclass
aquafer <- MTBE$Aquifier
ph <- MTBE$pH
welldepth <- MTBE$Depth
do2 <- MTBE$DissOxy
d2f <- MTBE$Distance
pind <- MTBE$IndPct
detet <- MTBE$MTBEDetect
wellclass <- as.numeric(as.factor(wellclass)) - 1
aquafer <- as.numeric(as.factor(aquafer)) - 1                                                                               
detet <- as.numeric(as.factor(detet)) - 1
mtbe.lmCoded <- glm(detet ~ wellclass+aquafer+ph+welldepth+do2+d2f+pind)
model = step(mtbe.lmCoded,direction='both')
model
plot(model)
step(mtbe.lmCoded,direction='forward',trace =1)


pchisq(model$deviance, model$df.residual)
```

```{r}
model = glm(formula = detet ~ pind + welldepth)
summary(model)
```
#28
```{r}
load("BONDING.Rdata")
View(BONDING)
```

```{r}
#smartbond = 1 , composite = 0
BONDING$ADHESIVE
adhesive <- as.numeric(as.factor(BONDING$ADHESIVE))-1
adhesive
model = glm(adhesive~BONDING$ARISCORE)
summary(model)
pchisq(model$deviance, model$df.residual)
logLik(model)
```
















