---
title: "HCH6"
output: html_notebook
---
setup


Jonathan Dombrowski 
Math 424

Question 6

Characteristics of sea ice melt ponds. Surface
albedo is defined as the ratio of solar energy
directed upward from a surface over energy inci-
dent upon the surface. Surface albedo is a critical
climatological parameter of sea ice. The National
Snow and Ice Data Center (NSIDC) collects data
on the albedo, depth, and physical characteristics
of ice melt ponds in the Canadian Arctic, includ-
ing ice type (classified as first-year ice, multiyear
ice, or landfast ice). Data for 504 ice melt ponds
located in the Barrow Strait in the Canadian Arctic
are saved in the PONDICE file. Environmental
engineers want to model the broadband surface
albedo level, y, of the ice as a function of pond
depth, x 1 (meters), and ice type, represented by the
dummy variables x 2 = {1 if first-year ice, 0 if not}
and x 3 = {1 if multiyear ice, 0 if not}. Ultimately,
the engineers will use the model to predict the
surface albedo level of an ice melt pond. Access the
data in the PONDICE file and identify the experi-
mental region for the engineers. What advice do you
give them about the use of the prediction equation?


```{r}
y = PONDICE$broadbandalb
x1 = PONDICE$depth
x2 = PONDICE$icetype

t1 = subset(PONDICE, icetype ==1 )
t2 = subset(PONDICE, icetype ==2 )
t3 = subset(PONDICE, icetype ==3 )

min(t1$depth)
max(t1$depth)
min(t2$depth)
max(t2$depth)
min(t3$depth)
max(t3$depth)
```




VIF
```{r}
library(usdm)
temp = factor(PONDICE$icetype)
levels(temp) = c("not","1stYear","multiYear") 
PONDICE$icetype.f = factor(PONDICE$icetype)
test = data.frame(PONDICE$broadbandalb, PONDICE$depth, PONDICE$icetype.f)
vif(test)
```



Creating a correllogram for the data set:

```{r}
library(corrplot)
corrplot.mixed(cor(reorPondice),  tl.col="black")
```
We notice that there is a very high correlation between x1 and x5, they seem to be collinear. Y and x4 see to be collinear as well. The respective 0.99 and 0.95 $\hat R^2$ values show that we need to remove x1 and x4 from the model as they are collinear.

Fixing the model 
```{r}
model = lm(PONDICE$broadbandalb~.,data = PONDICE)
summary(model)
```

QUESTION 19 

Cooling method for gas turbines. Refer to the
Journal of Engineering for Gas Turbines and
Power (January 2005) study of a high-pressure
inlet fogging method for a gas turbine engine,
Exercise 6.10 (p. 343). Recall that a number of
independent variables were used to predict the
heat rate (kilojoules per kilowatt per hour) for
each in a sample of 67 gas turbines augmented
with high-pressure inlet fogging. For this exercise,
consider a first-order model for heat rate as a
function of the quantitative independent variables’
cycle speed (revolutions per minute), cycle pres-
sure ratio, inlet temperature ( ◦ C), exhaust gas
temperature ( ◦ C), air mass flow rate (kilograms
per second), and horsepower (Hp units). Theoret-
ically, the heat rate should increase as cycle speed
increases. In contrast, theory states that the heat
rate will decrease as any of the other independent
variables increase. The model was fit to the data in
the GASTURBINE file with the results shown
in the accompanying MINITAB printout. Do you
detect any signs of multicollinearity? If so, how
should the model be modified?

```{r}
rpm <- GASTURBINE$RPM
cpratio <- GASTURBINE$CPRATIO
inlettemp <- GASTURBINE$INLETTEMP
exhtemp <- GASTURBINE$EXHTEMP
airflow <- GASTURBINE$AIRFLOW
heatrate <-  GASTURBINE$POWER
power =GASTURBINE$POWER
```


first order model : rpm, cpr, intlettemp, exhtemp, airflow, power

```{r}
library(usdm)
data = data.frame(rpm,cpratio,inlettemp,exhtemp,airflow, power)
vif(data)
data = data.frame(rpm,cpratio,inlettemp,exhtemp,airflow)
vif(data)
data = data.frame(rpm,cpratio,exhtemp,airflow)
vif(data)
model = lm(heatrate~rpm+cpratio+exhtemp+airflow)

library(corrplot)
corrplot.mixed(cor(data.frame(heatrate,rpm,cpratio,exhtemp, airflow)))


model
summary(model)
```
```{r}
library(olsrr)
model1 = lm(heatrate~rpm+cpratio+exhtemp, data = GASTURBINE)
ols_stepwise(model = model1, pent = 0.15, prem=0.15)
summary(model1)
model1
```
 

Question 21

```{r}
load("HAMILTON.Rdata")
```
```{r}
y= HAMILTON$Y
x1=HAMILTON$X1
x2 = HAMILTON$X2
cor.test(y,x1)
cor.test(y,x2)
model = lm(y ~ x1 + x2 )
summary(model)

```
```{r}
cor.test(x1,x2)

summary(lm(y~x1))
summary(lm(y~x2))
library(usdm)
vif(HAMILTON)
```

















